Breast Cancer Diagnosis Classification Analysis

### 2022-12-09 powerpoint.rmd

```{r knn_tuning_plot, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() + geom_line(aes(x=type_two_error_knn$k, y=type_two_error_knn$error), size=1) + geom_line(aes(x=type_two_error_knn$k, y=type_two_error_knn$typetwoerror), size=1.5, color="#c82798") + labs(title = "KNN Type I and Overall Error", x = "K", y = "Error")
```

@@

```{r rf_tuning_plot, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() + geom_line(aes(x=type_two_error_rf$ntree, y=type_two_error_rf$error), size=1) + geom_line(aes(x=type_two_error_rf$ntree, y=type_two_error_rf$typetwoerror), size=1.5, color="#c82798") + labs(title = "Random Forrest Type I and Overall Error", x = "Number of Trees", y = "Error")
```

@@

@@

- Tuned neighbors value to `r neighbors_best`
- 2 False-Negatives
- `knn.err` % prediction accuracy

@@

- Tuned cost value to `r cost_best`
- 2 False-Negatives
- `svm.err` % prediction accuracy

@@

- 1 False-Negative
- `rf.err` % prediction accuracy

>>>>

```{r knn_tuning_plot, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() + geom_line(aes(x=type_two_error_knn$k, y=type_two_error_knn$error), size=1) + geom_line(aes(x=type_two_error_knn$k, y=type_two_error_knn$typetwoerror), size=1.5, color="#c82798") + labs(title = "KNN Type II and Overall Error", x = "K", y = "Error")
```

@@

```{r rf_tuning_plot, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() + geom_line(aes(x=type_two_error_rf$ntree, y=type_two_error_rf$error), size=1) + geom_line(aes(x=type_two_error_rf$ntree, y=type_two_error_rf$typetwoerror), size=1.5, color="#c82798") + labs(title = "Random Forrest Type II and Overall Error", x = "Number of Trees", y = "Error")
```

@@

```{r}
### Gathering Data

train$diagnosis <- as.factor(train$diagnosis)
test$diagnosis <- as.factor(test$diagnosis)
```

@@

- Tuned neighbors value to `r neighbors_best`
- 2 False-Negatives
- 96.04% prediction accuracy

@@

- Tuned cost value to `r cost_best`
- 2 False-Negatives
- 96.48% prediction accuracy

@@

- 1 False-Negative
- 95.15% prediction accuracy
